Manuscript figures

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 4 for revision

#################### Make the figure ##################
# Define colors
cols_lc <- tibble(
    cols = c('#ff7f00', '#074702', '#b2df8a',
             '#33a02c', '#3347f9', '#5a6057',
             '#fdbf6f'),
    `Land cover type` = c("Cropland", 'Forest/dense tree', 
                          "Grassland", 'Shrubland',  "Water", 
                          "Built-up", 'Bareland'),
    ids = as.factor(1:7))
# Satellite images
# Image of season 1
s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s1)[, 2:4]), 
               stretch = 'hist') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("NICFI (season 1)") +
    theme_void() +
    theme(plot.title = element_text(size = 10, hjust = 0.5),
          plot.margin = unit(rep(-0.1, 4),"cm"))

# Image of season 2
s2_fg <- ggRGB(nicfi_s2, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s2)[, 2:4]), 
               stretch = 'lin') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("NICFI (season 2)") +
    theme_void() +
    theme(plot.title = element_text(size = 10, hjust = 0.5),
          plot.margin = unit(rep(-0.1, 4),"cm"))

# Image of VV
# Slope, Cos(x), Intercept
vv_fg <- ggRGB(vv_coefs, r = 2, g = 4, b = 1, 
               scale = max(values(vv_coefs)[, c(2, 4, 1)]), 
               stretch = 'hist') +
    geom_sf(data = pts_example,
            color = 'white',
            size = 3) +
    geom_sf(data = pts_example,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("Sentinel-1 (VV)") +
    theme_void() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.title = element_text(size = 10, hjust = 0.5),
          plot.margin = unit(rep(-0.1, 4),"cm"))

# Image of VH
# Slope, Cos(x), Intercept
vh_fg <- ggRGB(vh_coefs, r = 2, g = 4, b = 1, 
               scale = max(values(vh_coefs)[, c(1, 2, 4)]), 
               stretch = 'lin') +
    geom_sf(data = pts_example,
            color = 'white',
            size = 3) +
    geom_sf(data = pts_example,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("Sentinel-1 (VH)") +
    theme_void() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.title = element_text(size = 10, hjust = 0.5),
          plot.margin = unit(rep(-0.1, 4),"cm"))

@@

ref_epl <- ggplot(pts_nicfi_all,
                  aes(x = Band, y = Reflectance / 1000,
                      color = ids)) +
    geom_point() + geom_line(show.legend = 'line') +
    ylab(bquote('Reflectance'~(10^3))) + 
    xlab("Band") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    scale_x_discrete(limit = factor(1:4),
                     labels = unique(pts_nicfi_all$`Band name`)) +
    theme_bw() +
    facet_wrap(~ Season, nrow = 2, 
               scales = "free_y",
               strip.position = "top") +
    theme(text = element_text(size = 11))

ts_epl <- ggplot() + 
    geom_point(data = pts_ts, 
               aes(x = DOY, y = `dB`, 
                   color = factor(ids)),
               size = 0.6) +
    geom_line(data = pts_fit,
              aes(x = DOY, y = `dB`, 
                  color = factor(ids))) +
    facet_wrap(~polarization, 
               scales = 'free_y', nrow = 2,
               strip.position = "top") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_bw() + theme(text = element_text(size = 11))

@@

ggsave(here('docs/figures/satellite_images.tiff'),
       fg, bg = "white", 
       width = 6, height = 6, dpi = 600)

# Figure 2, combination art
# Double column figure, 3740 * 3740 at 500 dpi
ggsave(here('docs/figures/figure2_satellite_images.tiff'),
       main_fg, bg = "white", units = "px", 
       width = 3740, height = 3740)
```

@@

# Sub-tiling figure
sub_tiling_fg <- ggplot(sub_tiling) + 
    geom_sf(data = sub_tiles, aes(fill = Usage),
            color = 'blue', lwd = 0.3) +
    scale_fill_manual(values = c('forestgreen', 'orangered')) +
    geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
    geom_sf_text(aes(label = index), size = 3) +
    theme_void() +
    theme(legend.position = 'bottom',
          plot.title = element_text(hjust = -0.15, vjust = -6),
          plot.margin = unit(rep(0, 4),"cm"))

@@

# Ensemble plots
## Legend
r_df <- data.frame(x = 1:7, 
                   y = 1:7,
                   rst = as.factor(1:7))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    scale_fill_manual('Land cover',
                      values = c('#ff7f00', '#074702', '#b2df8a',
                                 '#33a02c', '#3347f9', '#5a6057',
                                 '#fdbf6f'), 
                      breaks = 1:7,
                      labels = c("Cropland", 'Forest/Dense tree', "Grassland", 
                                 'Shrubland',  "Water", "Built-up",
                                 'Bareland')) +
    theme_minimal() +
    theme(legend.position = 'right',
          plot.margin = unit(rep(0, 4),"cm"))+
    guides(fill = guide_legend(ncol = 2))

@@

esb_fg <- ggarrange(plotlist = plots_esb, ncol = 4,
                    labels = sub_tiles$index,
                    font.label = list(size = 12, color = "black", 
                                   face = "plain"),
                    hjust = -3, vjust = 0.1)
guess_fg <- ggarrange(plotlist = plots_guess, ncol = 4)
refine_fg <- ggarrange(plotlist = plots_refine, ncol = 4)

@@

# Plot
plot_img <- function(rst, bry){
    # plot
    ggRGB(rst, r = 1, g = 2, b = 3, 
          scale = max(values(rst)),
          stretch = 'hist') +
        geom_sf(data = bry, 
                color = 'blue', fill = NA,
                lwd = 0.4) +
        theme_void() +
        theme(plot.title = element_text(size = 10, hjust = 0.5),
              plot.margin = unit(rep(-0.1, 4),"cm"))
}
s1_plots <- lapply(1:length(images), function(n) {
    nm <- names(images)[n]
    bry <- sub_tiles %>% filter(index == nm) %>% 
        st_transform(crs = crs(images[[n]]))
    rst <- subset(images[[n]], c(4, 3, 2)) # 1, 2, 3
    plot_img(rst, bry)
})
s1_fg <- ggarrange(plotlist = s1_plots, ncol = 4)

@@

fgs <- ggarrange(esb_fg, guess_fg, refine_fg, s1_fg, s2_fg, nrow = 5,
                 labels = c('A', 'B', 'C', "S1", "S2"),
                 font.label = list(size = 12, color = "black", 
                                   face = "plain"),
                 hjust = 0.9, vjust = 6)
labels_fg <- ggarrange(NULL, fgs, sub_tiling_fg, 
                       ncol = 3, widths = c(0.1, 2, 1)) +
    theme(plot.margin = margin(0.3, 0 ,0, 0, "cm"))

ggsave(here('docs/figures/labels.tiff'),
       labels_fg, bg = "white",
       width = 8, height = 6.5, dpi = 600)
```

>>>>

#################### Make the figure ##################
# Define colors
cols_lc <- tibble(
    cols = c('#ff7f00', '#074702', '#b2df8a',
             '#33a02c', '#3347f9', '#5a6057',
             '#fdbf6f'),
    `Land cover type` = c("Cropland", 'Forest/dense tree', 
                          "Grassland", 'Shrubland',  "Water", 
                          "Built-up", 'Bareland'),
    ids = as.factor(1:7))
# Satellite images
# Image of season 1
s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s1)[, 2:4]), 
               stretch = 'hist') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("NICFI (season 1)") +
    theme_void() +
    theme(plot.title = element_text(size = 12, hjust = 0.5),
          plot.margin = unit(c(-0.1, rep(-0.5, 3)),"cm"))

# Image of season 2
s2_fg <- ggRGB(nicfi_s2, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s2)[, 2:4]), 
               stretch = 'lin') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("NICFI (season 2)") +
    theme_void() +
    theme(plot.title = element_text(size = 12, hjust = 0.5),
          plot.margin = unit(c(-0.1, rep(-0.5, 3)),"cm"))

# Image of VV
# Slope, Cos(x), Intercept
vv_fg <- ggRGB(vv_coefs, r = 2, g = 4, b = 1, 
               scale = max(values(vv_coefs)[, c(2, 4, 1)]), 
               stretch = 'hist') +
    geom_sf(data = pts_example,
            color = 'white',
            size = 3) +
    geom_sf(data = pts_example,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("Sentinel-1 (VV)") +
    theme_void() +
    theme(plot.title = element_text(size = 12, hjust = 0.5),
          plot.margin = unit(c(-0.1, rep(-0.5, 3)),"cm"))

# Image of VH
# Slope, Cos(x), Intercept
vh_fg <- ggRGB(vh_coefs, r = 2, g = 4, b = 1, 
               scale = max(values(vh_coefs)[, c(1, 2, 4)]), 
               stretch = 'lin') +
    geom_sf(data = pts_example,
            color = 'white',
            size = 3) +
    geom_sf(data = pts_example,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("Sentinel-1 (VH)") +
    theme_void() +
    theme(plot.title = element_text(size = 12, hjust = 0.5),
          plot.margin = unit(c(-0.1, rep(-0.5, 3)),"cm"))

@@

ref_epl <- ggplot(pts_nicfi_all,
                  aes(x = Band, y = Reflectance / 1000,
                      color = ids)) +
    geom_point(size = 1.6) + geom_line(show.legend = 'line', size = 0.8) +
    ylab(bquote('Reflectance'~(10^3))) + 
    xlab("Band") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    scale_x_discrete(limit = factor(1:4),
                     labels = unique(pts_nicfi_all$`Band name`)) +
    theme_bw() +
    facet_wrap(~ Season, nrow = 2, 
               scales = "free_y",
               strip.position = "top") +
    theme(text = element_text(size = 14),
          legend.text = element_text(size = 13))

ts_epl <- ggplot() + 
    geom_point(data = pts_ts, 
               aes(x = DOY, y = `dB`, 
                   color = factor(ids)),
               size = 1.6) +
    geom_line(data = pts_fit,
              aes(x = DOY, y = `dB`, 
                  color = factor(ids)),
              size = 0.8) +
    facet_wrap(~polarization, 
               scales = 'free_y', nrow = 2,
               strip.position = "top") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_bw() + theme(text = element_text(size = 14),
          legend.text = element_text(size = 13))

@@

# Figure 2, combination art
# 1.5 column figure, 2756 * 2500 at 500 dpi
ggsave(here('docs/figures/figure2_satellite_images.tiff'),
       fg, bg = "white", units = "px", 
       width = 2756, height = 2500)
```

@@

# Sub-tiling figure
sub_tiling_fg <- ggplot(sub_tiling) + 
    geom_sf(data = sub_tiles, aes(fill = Usage),
            color = 'blue', lwd = 0.3) +
    scale_fill_manual(values = c('forestgreen', 'orangered')) +
    geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
    geom_sf_text(aes(label = index), size = 5) +
    theme_void() +
    theme(legend.position = 'bottom',
          text = element_text(size = 17),
          plot.title = element_text(hjust = -0.15, vjust = -6),
          plot.margin = unit(rep(0, 4),"cm"))

@@

# Ensemble plots
## Legend
r_df <- data.frame(x = 1:7, 
                   y = 1:7,
                   rst = as.factor(1:7))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    scale_fill_manual('Land cover',
                      values = c('#ff7f00', '#074702', '#b2df8a',
                                 '#33a02c', '#3347f9', '#5a6057',
                                 '#fdbf6f'), 
                      breaks = 1:7,
                      labels = c("Cropland", 'Forest/Dense tree', "Grassland", 
                                 'Shrubland',  "Water", "Built-up",
                                 'Bareland')) +
    theme_minimal() +
    theme(legend.position = 'right',
          text = element_text(size = 17),
          plot.margin = unit(rep(0, 4),"cm"))+
    guides(fill = guide_legend(ncol = 2))

@@

esb_fg <- ggarrange(plotlist = plots_esb, ncol = 4,
                    labels = sub_tiles$index,
                    font.label = list(size = 16, color = "black", 
                                   face = "plain"),
                    hjust = -3, vjust = 0.25)
guess_fg <- ggarrange(plotlist = plots_guess, ncol = 4)
refine_fg <- ggarrange(plotlist = plots_refine, ncol = 4)

@@

# Plot
plot_img <- function(rst, bry){
    # plot
    ggRGB(rst, r = 1, g = 2, b = 3, 
          scale = max(values(rst)),
          stretch = 'hist') +
        geom_sf(data = bry, 
                color = 'blue', fill = NA,
                lwd = 0.4) +
        theme_void() +
        theme(plot.margin = unit(rep(-0.1, 4),"cm"))
}
s1_plots <- lapply(1:length(images), function(n) {
    nm <- names(images)[n]
    bry <- sub_tiles %>% filter(index == nm) %>% 
        st_transform(crs = crs(images[[n]]))
    rst <- subset(images[[n]], c(4, 3, 2)) # 1, 2, 3
    plot_img(rst, bry)
})
s1_fg <- ggarrange(plotlist = s1_plots, ncol = 4)

@@

fgs <- ggarrange(esb_fg, guess_fg, refine_fg, s1_fg, s2_fg, nrow = 5,
                 labels = c('A', 'B', 'C', "S1", "S2"),
                 font.label = list(size = 16, color = "black", 
                                   face = "plain"),
                 hjust = 0.9, vjust = 6)
labels_fg <- ggarrange(NULL, fgs, sub_tiling_fg, 
                       ncol = 3, widths = c(0.1, 2, 1)) +
    theme(plot.margin = margin(0.3, 0 ,0, 0, "cm"))

# Figure 4, combination art
# 2 column figure, 3150 * 2560 at 500 dpi
ggsave(here('docs/figures/figure4_labels_example.tiff'),
       labels_fg, bg = "white", units = "px", 
       width = 3150, height = 2560)
```
